\textbf{\sc Towards Deliberative Control of Autonomous Robots}

### 2012-02-16 concepts.tex
rearranging text from concepts into europa-basics
smoother transition into "europa's plan representation" section

This section describes the fundamental entities within \eu which are
typical to other CAIP-based formalisms.

@@

We have just covered the main elements of \eu's planning
representation:

\begin{enumerate}
\item \textbf{Domains, Variables and Objects} to represent the
  entities (Objects) and attributes (Variables) needed to represent a
  problem domain

\item \textbf{Tokens} Temporally scoped predicates to represent states
  and actions in time.

\item \textbf{Token States} which are necessary for the implementation
  of planning operations on a partial plan.

\item \textbf{Constraints} to describe relationships among attributes
  of objects and tokens. \eu has a built-in library of constraints
  that covers time, resources and others that are common in real life
  problem domains.

\item \textbf{Domain Rules} to describe internal and external
  relationships on and between tokens respectively. Rules are applied
  to active tokens (master tokens) referred to as masters and
  typically produce inactive tokens (slaves) which are a key vehicle
  through which the planning process evolves. \comment{citation, or
    perhaps remove this statement?:}The rule structure in \eu differs
  from the more restrictive commitment to preconditions and effects in
  classical planning which prohibits durative actions and disembodied
  effects (i.e. effects which may not occur until some temporal
  distance after the end of the action).

\item \textbf{Timelines and Resources} are built in implementations of
  Object types that appear frequently in real life domains.

>>>>

\eu follows the representation outlined by the CAIP framework, it also adds a few elements to it that are necessary for an efficient implementation of constraint-based planning. Below is a brief summary of the main elements, followed by a detailed description for each one:

\begin{enumerate}
\item \textbf{Tokens} Temporally scoped entities that correspond to Intervals in the CAIP framework, are used to represent  state and actions in time. A\textbf{Token State model} is defined to support an efficient implementation of plan-space search algorithms.

\item \textbf{Domains, Variables and Constraint} are used to represent restrictions in the problem domain in terms of a CP formulation.

\item \textbf{Domain Rules} are used to describe internal and external relationships on and between tokens, as presecribed by the CAIP framework.

\item \textbf{Objects} are used to represent problem domains in a more modular and scaleable way. \textbf{Timelines and Resources} are built in implementations of Object types that appear frequently in real life domains.

@@
